### 2023-04-19 definitions.tex
section 2

Let us recall that a {\em vector addition system with states (VASS)} in dimension $d$ ($d$-VASS for short) is a finite $\mathds{Z}^d$-labeled directed graph $V = (Q,T)$, where $Q$ is the set of {\em control-states}, and where $T \subseteq Q \times \mathds{Z}^d \times Q$ is the set of {\em control-transitions}. 
% The {\em size} of $V$ is defined as $|V|=|Q|+|T|*d*|log(||T||)$ where $||T||$ denotes the absolue value of the largest number that appears in $T$, i.e. $||T|| = max\{ ||\textbf{z}||: (p,\textbf{z},q) \in T\}$.

Subsetquently, $Q \times \N^d$ is the set of configurations of $V$.
For every configuration $p(\textbf{u}), q(\textbf{v}) \in Q \times \N^d$ and every control-transition $t = (p, \textbf{z}, q)$ we write $p(\textbf{u}) \xrightarrow{t} q(\textbf{v})$ whenever $\textbf{v} = \textbf{u} + \textbf{z} \geq \textbf{0}$
%
\iffalse \mathieu{Defining it like this makes it a LTS rather than a unlabeled TS - maybe talk about how we can 'forget' the labels to obtain an unlabeled TS ?}
\alain{les VASS ne sont pas vraiment étiquetés, sauf si on veut le faire, car on peut dire que les VASS sont définis à partir d'un nombre fini de control-transitions  $t = (p, \textbf{z}, q)$ générant une infinité de transtions notées $p(\textbf{u}) \xrightarrow{t} q(\textbf{v})$ puisque pour tout s, $p(\textbf{u+s}) \xrightarrow{t} q(\textbf{v+s})$} \fi
When in the context of a $d$-VASS, we denote $0^d$ by $\textbf{0}$.

>>>>

Let us recall that a {\em vector addition system with states (VASS)} in dimension $d$ ($d$-VASS for short) is a finite $\mathds{Z}^d$-labeled directed graph $V = (Q,T)$, where $Q$ is the set of {\em control-states}, and where $T \subseteq Q \times \mathds{Z}^d \times Q$ is the set of {\em control-transitions}. 
% The {\em size} of $V$ is defined as $|V|=|Q|+|T|*d*|log(||T||)$ where $||T||$ denotes the absolue value of the largest number that appears in $T$, i.e. $||T|| = max\{ ||\textbf{z}||: (p,\textbf{z},q) \in T\}$.
%
Subsetquently, $Q \times \N^d$ is the set of configurations of the transition system associated with $V$.
For all configurations $p(\textbf{u}), q(\textbf{v}) \in Q \times \N^d$ and for every control-transition $t = (p, \textbf{z}, q)$ we write $p(\textbf{u}) \xrightarrow{t} q(\textbf{v})$ whenever $\textbf{v} = \textbf{u} + \textbf{z} \geq \textbf{0}$
%
\iffalse \mathieu{Defining it like this makes it a LTS rather than a unlabeled TS - maybe talk about how we can 'forget' the labels to obtain an unlabeled TS ?}
\alain{les VASS ne sont pas vraiment étiquetés, sauf si on veut le faire, car on peut dire que les VASS sont définis à partir d'un nombre fini de control-transitions  $t = (p, \textbf{z}, q)$ générant une infinité de transtions notées $p(\textbf{u}) \xrightarrow{t} q(\textbf{v})$ puisque pour tout s, $p(\textbf{u+s}) \xrightarrow{t} q(\textbf{v+s})$} \fi
When in the context of a $d$-VASS, we denote $0^d$ by $\textbf{0}$.
